---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# uwebasr2

<!-- badges: start -->
<!-- badges: end -->

The goal of uwebasr2 is to provide access to UWebASR API for audio transcription.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("skvrnami/uwebasr2")
```

## Usage

```{r example}
library(uwebasr2)
```

The library contains two functions that provide access to UWebASR API: `uwebasr_post` and `uwebasr_get`.

Both of the functions have similar parameters: 

- `lang_model` - Language model that is to be used for speech transcription. The available
models are `CZ` for Czech language model and `SK` for Slovak language model. 
- `file_path` (in the case of `uwebasr_post`) / `audio_url` (in the case of `uwebasr_get`) - path or URL to the audio. 
- `format` - Format of the output. Available formats include: `plaintext` (default option) and `json`.
The API also accepts formats `trs`, `extended_trs` and `webvtt`, but the working of the package is not tested for using these formats. 

The `uwebasr_post` uploads file from local filesystem to the API and returns the transcription.

```{r}
babis_dopis <- uwebasr_post(lang_model = "CZ", "babis_dopis.mp3")
cat(babis_dopis)
```

```{r, eval=FALSE}
# Doesn't work for some reason
grospic_intro <- uwebasr_get("CZ", "http://skvrnami.github.io/uwebasr/grospic.mp3", "plaintext")
cat(grospic_intro)
```

